What to simulate? Inferring the right direction for mental rotation

### 2014-02-07 man/cogsci-2014/cogsci-2014.tex
Add histogram figure to paper

@@

\begin{figure*}[t]
  \begin{center}
    \includegraphics[width=\textwidth]{../../figures/D/model-traces.pdf}
    \caption{\textbf{Example stimuli and model behavior.} On the left
      are two stimulus pairs, one ``same'' (top) and one ``flipped''
      (bottom), both with a rotation of $120^\circ$. The grey plots
      show the actions that each model took for these stimuli. The
      color of each point (action) indicates whether the model's
      current mental image was generated under the hypothesis that the
      objects are the same (red) or flipped (blue). The similarity
      functions for each of these hypotheses are shown on the right.}
    \label{fig:model-traces}
  \end{center}
\end{figure*}

@@

>>>>

\begin{figure*}[t]
  \begin{center}
    \includegraphics[width=\textwidth]{../../figures/D/model-traces.pdf}
    \caption{\textbf{Example stimuli and model behavior.} On the left
      is a ``flipped'' stimulus pair with a rotation of
      $120^\circ$. The grey plots show the actions that each model
      took for this stimulus. The color of each point (action)
      indicates whether the model's current mental image was generated
      under the hypothesis that the objects are the same (red) or
      flipped (blue). The similarity functions for each of these
      hypotheses are shown on the right.}
    \label{fig:model-traces}
  \end{center}
\end{figure*}

@@

@@

\begin{figure*}[t]
  \begin{center}
    \includegraphics[width=\textwidth]{../../figures/D/response_time_histograms.pdf}
    \caption{\textbf{Response time histograms.} Each subplot shows a
      histogram of RTs for people (left) or one of the models (only
      for trials which were answered correctly).}
    \label{fig:histograms}
  \end{center}
\end{figure*}
